API design for machine learning software: experiences from the scikit-learn project

### 2013-10-18 paper.tex
Move model selection snippet.
Copy edit advanced API.

As introduced in Section~\ref{sec:estimators}, hyper-parameters set in the
constructor of an estimator
determine the behavior of the learning algorithm
and hence the performance of the resulting model on unseen data.
The problem of \textit{model selection} is therefore to find, within
some hyper-parameter space, the best combination of hyper-parameters, with
respect to some user-specified criterion. For example, a decision
tree with too small a value for the maximal tree depth
parameter will tend to underfit, while too large a value will make it overfit.

In \sklearn, model selection is supported by the meta-estimators
\texttt{GridSearchCV} and \texttt{RandomizedSearchCV}.  These take as input an
estimator (basic or composite), whose hyper-parameters must be optimized, and a
set of hyperparameter settings to search through.
This set is represented as a mapping of parameter names
to a set of discrete choices in the case of grid search,
which exhaustively enumerates the ``grid'' (cartesian product)
of complete parameter combinations.
Randomized search is a smarter algorithm
that avoids the combinatorial explosion in grid search
by sampling a fixed number of times from its parameter distributions
\citep{bergstra2012}.

>>>>

As introduced in Section~\ref{sec:estimators}, hyper-parameters set in the
constructor of an estimator
determine the behavior of the learning algorithm
and hence the performance of the resulting model on unseen data.
For example, a decision
tree with too small a value for the maximal tree depth
parameter will tend to underfit, while too large a value will make it overfit.
The problem of \textit{model selection} is therefore to find, within
some hyper-parameter space, the best combination of hyper-parameters, with
respect to some user-specified criterion.

In \sklearn, model selection is supported by the meta-estimators
\texttt{GridSearchCV} and \texttt{RandomizedSearchCV}.  These take as input an
estimator (basic or composite), whose hyper-parameters must be optimized, and a
set of hyperparameter settings to search through.
This set is represented as a mapping of parameter names
to a set of discrete choices in the case of grid search,
which exhaustively enumerates the ``grid'' (cartesian product)
of complete parameter combinations.
Randomized search is a more efficient algorithm
that avoids the combinatorial explosion in grid search
by sampling a fixed number of times from its parameter distributions
\citep{bergstra2012}.
